The force-free magnetosphere of a Kerr black hole: the role of boundary conditions

### 2018-06-30 paper/ms.tex
state

@@

The analysis of Section \ref{subsec:features}

@@

In this paper, we revisit the problem of the uniform field solution to the BZ mechanism.

>>>>

The Blandford-Znajek (BZ) mechanism \cite{Blandford1977} is believed to be
one of most efficient ways to extract rotation energy from spinning black holes (BHs),
which operates in BH systems on all mass scales, from the stellar-mass BHs of gamma-ray
bursts to the supermassive BHs of active galactic nuclei. In the past decade,
we have studied the BZ mechanism from different approaches and the cross-check among
these different approaches has facilitate substantial progress in understanding the underlying
detailed physics in the BZ mechanism. Taking the simple monopole magnetic field
configuration as an example, the solutions obtained from different approaches
are in quantitative agreement,  see e.g.\cite{Komissarov2001,Komissarov2004,Komissarov2004e, McKinney2004}
for general relativistic magnetohydrodynamic simulations,
\cite{Tanabe2008,Pan2015,Pan2015b, Gralla2014, Gralla2015, Penna2015} for analytic solutions
and \cite{Contopoulos2013,Nathanail2014,Mahlmann2018} for numerical solutions.

But for other magnetic field configurations, there is no such good agreement, e.g.,
different approaches do even reach a consensus on the solution uniqueness for uniform field configuration.
Several force-free electrodynamic simulation \cite{Komissarov2004e, Komissarov2005,
Komissarov2007,Palenzuela2010,Paschalidis2013, Yang2015,Carrasco2017} have been done
for investigating this problem. Among these simulations, the BH magnetospheres
all settle down to a steady state with similar field configuration.

Analytic \cite{Yang2015}

GS equation, one LS, two eigen functions  radiation condition \cite{Pan2017}

Recent sims, radiation condition and the equatorial boundary condition

@@

Numerical solutions for the general parabola field configuration are out of scope of this paper.
The analysis of Section \ref{subsec:features} which is based on the radiation condition
and the marginally force-free equatorial boundary condition.

@@

In the force-free limit, the structure of steady and axisymmetric BH magnetosphere is governed by
the GS equation, which is a second-order differential equation about the magnetic flux $\Ap$, with two
free functions $\Omega(\Ap)$ and $I(\Ap)$ to be determined by . For the uniform field configuration, there is only one
LS, which is insufficient for determine both  $\Omega(\Ap)$ and $I(\Ap)$.
Therefore the solution uniqueness has been a controversial problem.
Recent high-accuracy force-free simulations done in Ref. \cite{East2018}
undoubtedly show that the two functions are not independent;
instead they are related by the radiation condition (\ref{eq:rad}).
In addition, an equatorial current sheet within the ergosphere was readily confirmed
in the simulations

In this paper, we revisit the problem of the uniform field solution.
From the radiation condition (\ref{eq:rad}) and the marginally force-free boundary
condition (\ref{eq:bc3}), we derive the
